State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-12 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Changed title of Section 9 to Improving Software Qualities
Revisions to section 10 (Recommendations)

\section{Software Qualities}\label{sec:sq}

@@

We provide specific recommendations for future consideration -- these are
not criticisms of past and/or current development practices. We
expand on some of the ideas from our interviews, and bring in further ideas
that could have a noticable impact. The ``new'' ideas are not novel to this
paper but rather from the software engineering and software carpentry domains
that have yet to have seen wide adoption.  We list the ideas roughly in the
order of increasing implementation effort.

@@

Multiple pain points encountered, especially technology hurdles
(\ppref{P_TechnologyHurdles}), could be alleviated by moving to a web
application. But this must be an active decision as it may not be a good
fit in all cases.  The decision needs to be based on whether, on balance, this
would improve the four factors identified earlier: compatibility,
maintainability, performance, and security. We outline the factors to consider
to enable better decision making, as a final decision crucially depends on
each teams' objectives.

@@

%JC: I'm aware of too many caveats wrt this recommendation, so I am taking
% it out.
%
%\item \textbf{Remove privacy from sensitive data.} For data with sensitive
%information, a team can ask the data owner to remove such information or add
%noise to protect privacy. One example is using de-identified copies of medical
%images for testing.

@@

Linters are simple tools that analyzes code to find programming errors,
suspicious constructs, and stylistic inconsistencies \cite{Wikipedia2022_Lint}.
While they can be used in an ad hoc fashion, coupling them with CI is where
the largest gain happens. Automatic use of code quality tools is increasing
commonplace for industrial software -- it is regretable that the
research software guidlines have no caught up to this.

@@

 Although the advice to modularize research software to handle
complexity is common \cite{WilsonEtAl2014, StewartEtAl2017, Storer2017},
specific guidelines on how to divide the software into modules is less
prevalent.  Not every decomposition is a good design for supporting change, as
shown by \cite{Parnas1972a}.  For instance, a design with low cohesion and high
coupling \cite[p.\ 48]{GhezziEtAl2003} will make change difficult. Especially in
research software, where change is inevitable, designers need to produce a
modularization that supports change.  Ocean modelling software is currently
feeling the pain of not emphasizing modularization in legacy code
\cite{JungEtAl2022}.

>>>>

\section{Improving Software Qualities}\label{sec:sq}

@@

We provide specific recommendations for future consideration -- these are not
criticisms of past and/or current development practices. We expand on some of
the ideas from our interviews, and bring in further ideas that could have a
noticeable impact. The ``new'' ideas are not novel to this paper but rather from
the software engineering and software carpentry domains, but have not yet seen
wide adoption.  We list the ideas roughly in the order of increasing
implementation effort.

@@

Multiple pain points, especially technology hurdles
(\ppref{P_TechnologyHurdles}), could be alleviated by moving to a web
application. However, this must be an active decision as it may not be a good
fit in all cases.  The decision needs to be based on whether, on balance, this
would improve the four factors identified earlier: compatibility,
maintainability, performance, and security. The following considerations may
help a team make a decision about the move to web applications:

@@

%JC: I'm aware of too many caveats wrt this recommendation, so I am taking
% it out.
%SS: okay, I agree.
%
%\item \textbf{Remove privacy from sensitive data.} For data with sensitive
%information, a team can ask the data owner to remove such information or add
%noise to protect privacy. One example is using de-identified copies of medical
%images for testing.

@@

Linters are simple tools that analyze code to find programming errors,
suspicious constructs, and stylistic inconsistencies \cite{Wikipedia2022_Lint}.
While they can be used in an ad hoc fashion, coupling them with CI is where
the largest gain happens. Automatic use of code quality tools is increasing
commonplace for industrial software -- it is regrettable that the
research software guidelines have no caught up to this.

@@

Although the advice to modularize research software to handle
complexity is common \cite{WilsonEtAl2014, StewartEtAl2017, Storer2017},
specific guidelines on how to divide the software into modules is less
prevalent.  Not every decomposition is a good design for supporting change, as
shown by Parnas~\cite{Parnas1972a}.  For instance, a design with low cohesion and high
coupling \cite[p.\ 48]{GhezziEtAl2003} will make change difficult. Especially in
research software, where change is inevitable, designers need to produce a
modularization that supports change.  Ocean modelling software is currently
feeling the pain of not emphasizing modularization in legacy code
\cite{JungEtAl2022}.
